MiP4

### 2018-05-22 MiP4.Rmd
panel modeling

```{r data import, include=FALSE}
# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
# http://epstein.wustl.edu/research/LPE.Alt.pdf
AltLassen <- read_dta("data/Replication/AltLassenJLEO.dta")

@@

```{r data wrangling}
# Combining Barber and ICS 
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

@@

```{r modeling, echo=FALSE}
#Next: Panel model of corruption against unemployment and high school? 
testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel01)

@@

>>>>

```{r data import, include=F}
# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
# http://epstein.wustl.edu/research/LPE.Alt.pdf
AltLassen <- read_dta("data/Replication/AltLassenJLEO.dta")

@@

```{r panel data wrangling, include=F}
# Combining Barber and ICS 
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

@@

```{r panel modeling, include=F}
#Next: Panel model of corruption against unemployment and high school? 
testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel01)

@@

```{r DiD wrangling, include=F}
# Creating DiD dataframe 
AltBarberDiD <- transform(BarberICC, ind_limits_2010_d = ave(ind_limits_2010, st, FUN = function(x) c(NA, diff(x))))
AltBarberDiD <- transform(AltBarberDiD, ind_limits_dummy_d = ave(ind_limits_dummy , st, FUN = function(x) c(NA, diff(x))))
AltBarberDiD <- transform(AltBarberDiD, pac_limits_2010_d = ave(pac_limits_2010, st, FUN = function(x) c(NA, diff(x))))
AltBarberDiD <- transform(AltBarberDiD, pac_limits_dummy_d = ave(pac_limits_dummy, st, FUN = function(x) c(NA, diff(x))))
AltBarberDiD <- transform(AltBarberDiD, ind2pty_limits_2010_d = ave(ind2pty_limits_2010, st, FUN = function(x) c(NA, diff(x))))
AltBarberDiD <- transform(AltBarberDiD, ind2pty_limits_dummy_d = ave(ind2pty_limits_dummy, st, FUN = function(x) c(NA, diff(x))))

AltBarberDiD %>% select(1:2,8,11,3:7,12:21) -> DiDsmall 
```

```{r DiD modeling, include=F}
